---
title: An Example R Markdown Document
subtitle: (A Subtitle Would Go Here if This Were a Class)
author: Steven V. Miller
institute: Department of Political Science
titlegraphic: /Dropbox/teaching/clemson-academic.png
fontsize: 10pt
output:
 beamer_presentation:
    template: ~/Dropbox/miscelanea/svm-r-markdown-templates/svm-latex-beamer.tex
    keep_tex: true
    latex_engine: pdflatex
#    dev: cairo_pdf # Use if latex_engine: xelatex
    slide_level: 2
make149: true
# mainfont: "Open Sans" # Try out some font options if xelatex
# titlefont: "Titillium Web" # Try out some font options if xelatex
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(fig.path='figs/')
knitr::opts_chunk$set(cache.path='cache/')

knitr::opts_chunk$set(
                  fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      }
                  )
```


# Pop Songs and Political Science

## Sheena Easton and Game Theory

Sheena Easton describes the following scenario for her baby:

1. Takes the morning train
2. Works from nine 'til five
3. Takes another train home again
4. Finds Sheena Easton waiting for him

Sheena Easton and her baby are playing a **zero-sum (total conflict) game**.

- Akin to Holmes-Moriarty game (see: von Neumann and Morgenstern)
- Solution: **mixed strategy**

## Rick Astley's Re-election Platform

Rick Astley's campaign promises:

- Never gonna give you up.
- Never gonna let you down.
- Never gonna run around and desert you.
- Never gonna make you cry.
- Never gonna say goodbye.
- Never gonna tell a lie and hurt you.

Whereas these pledges conform to the preferences of the **median voter**, we expect Congressman Astley to secure re-election.

## Caribbean Queen and Operation Urgent Fury

Billy Ocean released "Caribbean Queen" in 1984.

- Emphasized sharing the same dream
- Hearts beating as one

"Caribbean Queen" is about the poor execution of Operation Urgent Fury.

- Echoed JCS chairman David Jones' frustrations with military establishment.

Billy Ocean is advocating for what became the Goldwater-Nichols Act.

- Wanted to take advantage of **economies of scale**, resolve **coordination problems** in U.S. military.

## The Good Day Hypothesis

We know the following about Ice Cube's day.

1. The Lakers beat the Supersonics.
2. No helicopter looked for a murder.
3. Consumed Fatburger at 2 a.m.
4. Goodyear blimp: "Ice Cube's a pimp."

This leads to two different hypotheses:

- $H_0$: Ice Cube's day is statistically indistinguishable from a typical day.
- $H_1$: Ice Cube is having a good (i.e. greater than average) day.

These hypotheses are tested using archival data of Ice Cube's life.

# Example R code
## Example R stuff

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## ggplot code

```{r createdata, echo=TRUE, eval=FALSE}
df <- data.frame(x = rnorm(1000))
x <- df$x
base <- ggplot(df, aes(x)) + geom_density()  + scale_x_continuous(limits = c(-5, 5))
base + stat_function(fun = dnorm, colour = "red")
```


## Another Plot

```{r plotit, echo=FALSE}
library(ggplot2)
df <- data.frame(x = rnorm(1000))
x <- df$x
base <- ggplot(df, aes(x)) + geom_density()  + scale_x_continuous(limits = c(-5, 5))
base + stat_function(fun = dnorm, colour = "red")
```