---
title: An Example R Markdown Document
subtitle: (A Subtitle Would Go Here if This Were a Class)
author: Steven V. Miller
institute: Department of Political Science
titlegraphic: /Dropbox/teaching/clemson-academic.png
fontsize: 10pt
output:
 beamer_presentation:
    template: ../svm-latex-beamer.tex
    keep_tex: true
    latex_engine: xelatex # pdflatex also works here
    dev: cairo_pdf # I typically comment this out  if latex_engine: pdflatex
    slide_level: 3
make149: true
mainfont: "Open Sans" # Try out some font options if xelatex
titlefont: "Titillium Web" # Try out some font options if xelatex
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(fig.path='figs/')
knitr::opts_chunk$set(cache.path='cache/')

knitr::opts_chunk$set(
                  fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      }
                  )
library(tidyverse)
library(stevemisc)
```


# Pop Songs and Political Science

### Sheena Easton and Game Theory

Sheena Easton describes the following scenario for her baby:

1. Takes the morning train
2. Works from nine 'til five
3. Takes another train home again
4. Finds Sheena Easton waiting for him

### A Total Conflict Game Between Sheena Easton and Her Baby

|                         | Sheena Easton Stays Home       | Sheena Easton Goes to Baby's Work |
|-------------------------|---------------------|------------------|
| **Baby Home Again**          |  -100, **100**         |  **100**, 0       |
| **Baby Stays at Work**             |   **50**, 0        |  -100, **100**        |

Sheena Easton and her baby are playing a **zero-sum (total conflict) game**.

- Akin to Holmes-Moriarty game (see: von Neumann and Morgenstern)
- Solution: **mixed strategy**

### Rick Astley's Re-election Platform

Rick Astley's campaign promises:

- Never gonna give you up.
- Never gonna let you down.
- Never gonna run around and desert you.
- Never gonna make you cry.
- Never gonna say goodbye.
- Never gonna tell a lie and hurt you.

Are these promises (if credible) sufficient to secure re-election?

### 

```{r rick-astley-never-gonna-give-you-up-median-voter-theorem, eval = T, echo = F, fig.height=8.5, fig.width=14, message=F}

df <- data.frame(x = rnorm(1000))
x <- df$x

ggplot(df, aes(x)) + 
  theme_steve_web() +
  stat_function(fun = dnorm, colour = "black") +
  scale_x_continuous(limits = c(-4, 4), 
                     breaks = c(-4,  0,  4),
                     labels = c("Complete\nEmotional\nNeglect", 
                                "Never Gonna Give You Up\nLet You Down\nRun Around and Desert You\n(Preference of Median Voter)",
                                "Maximum\nEmotional\nSupport")) +
  geom_vline(xintercept = 0) +
  geom_vline(xintercept = 1, linetype="dashed") +
  geom_vline(xintercept = -2, linetype = "dashed") +
  geom_vline(xintercept = -.5, linetype = "dotted") +
  scale_y_continuous(limits = c(0, .5), breaks = NULL, label=NULL) +
  xlab("A Unidimensional Continuum of the Policy Space of Emotional Support") +
  ylab("") +
  stat_function(fun = dnorm, 
                xlim = c(-4,-2),
                size=0,
                geom = "area", fill="#f8766d", alpha=1) +
  stat_function(fun = dnorm, 
                xlim = c(1, 4),
                size=0,
                geom = "area", fill="#619cff", alpha=1)  +
  stat_function(fun = dnorm, 
                xlim = c(-.5, 1),
                size=0,
                geom = "area", fill="#619cff", alpha=.4) +
  stat_function(fun = dnorm, 
                xlim = c(-2, -.5),
                size=0,
                geom = "area", fill="#f8766d", alpha=.4) +
  annotate("text", label="Astley's rival is promising\nfar less in the (public?) good\nof emotional support",
           size = 3.5, family="Open Sans",
           x = -2.1, y = .4,
           hjust = 1) +
  annotate("text", 
           label="Congressman Astley is pledging\nmore emotional support\n(i.e. never gonna make you cry/say goodbye/tell a lie/hurt you)\nthan most his constituents want",
           size = 3.5, family="Open Sans",
           x = 1.1, y = .4,
           hjust = 0) +
  annotate("text", 
           label="Preferences\ncloser to\nAstley's\nrival",
           size = 3.5, family="Open Sans",
           x = -1.2, y = .45,
           hjust = .5) +
  annotate("text", 
           label="Preferences\ncloser to\nCongressman\nAstley",
           size = 3.5, family="Open Sans",
           x = .5, y = .45,
           hjust = .5) +
  labs(title = "Median Voter Theorem Suggests Congressman Astley Secures Re-election Against His Rival",
       subtitle = "Assuming a unidimensional policy space and single-peaked preferences, Congressman Astley is closer to the median voter than his rival and wins the election.") +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = -4)
  
  


```

### Rick Astley and Median Voter Theorem

Whereas these pledges conform to the preferences of the **median voter**, we expect Congressman Astley to secure re-election.

### Caribbean Queen and Operation Urgent Fury

Billy Ocean released "Caribbean Queen" in 1984.

- Emphasized sharing the same dream
- Hearts beating as one

"Caribbean Queen" is about the poor execution of Operation Urgent Fury.

- Echoed JCS chairman David Jones' frustrations with military establishment.

Billy Ocean is advocating for what became the Goldwater-Nichols Act.

- Wanted to take advantage of **economies of scale**, resolve **coordination problems** in U.S. military.

### The Good Day Hypothesis

We know the following about Ice Cube's day.

1. The Lakers beat the Supersonics.
2. No helicopter looked for a murder.
3. Consumed Fatburger at 2 a.m.
4. Goodyear blimp: "Ice Cube's a pimp."

### The Good Day Hypothesis

This leads to two different hypotheses:

- $H_0$: Ice Cube's day is statistically indistinguishable from a typical day.
- $H_1$: Ice Cube is having a good (i.e. greater than average) day.

These hypotheses are tested using archival data of Ice Cube's life.

### 

```{r good-day-hypothesis, eval = T, echo = F, fig.height=8.5, fig.width=14, message=F}
interval1 <- -qnorm((1-0.9)/2)  # 90% multiplier
interval2 <- -qnorm((1-0.95)/2) # 95% multiplier

tribble(
  ~variable, ~est, ~se,
  "Latent Estimate of\nIce Cube's Day", 1.6, .231
) %>%
  ggplot(.) + 
    theme_steve_web() +
  geom_hline(yintercept = .5, color = "red", lty=2) +
  geom_linerange(aes(x = variable, ymin = est - se*interval1,
                                ymax = est + se*interval1),
                            lwd = 1, position = position_dodge(width = 1/2)) +
  geom_pointrange(aes(x = variable, y = est, ymin = est - se*interval2,
                                 ymax = est + se*interval2),
                             lwd = 1/2, position = position_dodge(width = 1/2),
                             fill = "WHITE") +
  coord_flip() + xlab("") + ylab("Latent Estimate") +
  labs(title = "Latent Estimates from Ice Cube's Archives Lend Support to the 'Good Day' Hypothesis",
       subtitle = "Latent estimates are drawn from an item response model of indicators of the quality of Ice Cube's days. These include whether he had to use his A.K.",
       caption = "Data: Ice Cube's Archives, obviously fictional. Red value of .5 indicate likelihood of 'good day.'")
  


```